\chapter*{\sffamily Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}


First and foremost, I would like to express my sincerest gratitude to my thesis co-advisors, Ph.D. Andrés Marino Álvarez Meza and Ph.D. César Germán Castellanos Domínguez, as well as my thesis advisor, M.Sc. Bernardo Andrés Cardona Noreña. Your guidance, expertise, and commitment were fundamental to the completion of this work. Thank you for your dedication, patience, and unconditional support at every stage of this process.

I would also like to acknowledge the Control and Digital Signal Processing Group for their academic support. Your collaboration and contributions were key to the development of this research. To all of you, thank you for being part of this journey and helping me achieve this goal.

I also extend my deepest gratitude to my family, whose love, understanding, and constant emotional support motivated me to overcome every challenge faced during my academic training. Finally, but no less importantly, I wish to dedicate this work to the memory of Sahra and Braihan. Although they are no longer physically present, their friendship and unwavering support over so many years were essential to my journey. To both my family and the memory of my friends: without your backing, this achievement would not have been possible. I miss you both dearly.

Lastly, I would like to express my sincere gratitude to the project ``Sistema multimodal apoyado en juegos serios orientado a la evaluación e intervención neurocognitiva personalizada en trastornos de impulsividad asociados a TDAH como soporte a la intervención presencial y remota en entornos clínicos, educativos y comunitarios'' (Minciencias-92056). This research was made possible through the funding and support provided by the Universidad Nacional de Colombia and the Universidad Tecnológica de Pereira.


\begin{flushright}
  \studentname\\
  \issuedate
\end{flushright}